\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-29 popl-2019-journal-v/proving-full-abstraction.tex
Implement comment about ofes as sets with structure

% Cofe's
In the following, we present complete ordered family of equivalences \citep{di_gianantonio_2002}.
We loosely follow the presentation in \citet{birkedal_taste_2014} and introduce the necessary definitions needed for our particular world.
\begin{definition}[Ordered family of equivalences (o.f.e.)]
An \emph{ordered family of equivalences} is a pair $\cofe{X}$ where $X$ is a set and $\nequal$ is an equivalence relation for each $n$.
The pair must satisfy the following properties:
\begin{enumerate}
\item $\nequal[0]$ is the total relation.
\item For all $n \in \nats$, $\nequal[n] \supseteq \nequal[n+1]$.
\item For all $x,y \in X$,  if for all $n \in \nats$ $x \nequal y$, then $x = y$.
\end{enumerate}
\end{definition}
\dominique{Explain how an o.f.e. can be seen as a set with extra structure.}
\noindent The index on the family of equivalences is intuitively a measure of precision.
\dominique{Introduce phrases like ``up to n steps'' etc.}
The larger the index is, the more refined the equivalences are which means that they can distinguish more elements from one another.
On the other hand as the index decreases, the equivalences become increasingly imprecise and unable to distinguish certain elements.
At index 0, all precision is lost and the equivalence cannot distinguish anything.
% TODO: Lau write intuition for sequences and why they are necessary.
\begin{definition}[Complete ordered family of equivalences (c.o.f.e.)]
  \label{def:cauchy-sequence}
  A \emph{complete ordered family of equivalences} is an ordered family of equivalences
  $\cofe{X}$ such that every Cauchy sequence in $X$ has a limit
  in $X$.

>>>>

% Cofe's
In the following, we present complete ordered family of equivalences \citep{di_gianantonio_2002}.
We loosely follow the presentation in \citet{birkedal_taste_2014} and introduce the necessary definitions needed for our particular world.
\begin{definition}[Ordered family of equivalences (o.f.e.)]
An \emph{ordered family of equivalences} is a pair $\cofe{X}$ where $X$ is a set and $\nequal$ is an equivalence relation for each $n$.
The pair must satisfy the following properties:
\begin{enumerate}
\item $\nequal[0]$ is the total relation.
\item For all $n \in \nats$, $\nequal[n] \supseteq \nequal[n+1]$.
\item For all $x,y \in X$,  if for all $n \in \nats$ $x \nequal y$, then $x = y$.
\end{enumerate}
\end{definition}
\noindent An o.f.e.\ can be thought of as a set with extra structure.
Intuitively, the index on the family of equivalences is a measure of precision.
The larger the index is, the more refined the equivalences are which means that they can distinguish more elements from one another.
On the other hand as the index decreases, the equivalences become increasingly imprecise and unable to distinguish certain elements.
At index 0, all precision is lost and the equivalence cannot distinguish anything.
\dominique{Introduce phrases like ``up to n steps'' etc.}
% TODO: Lau write intuition for sequences and why they are necessary.
\begin{definition}[Complete ordered family of equivalences (c.o.f.e.)]
  \label{def:cauchy-sequence}
  A \emph{complete ordered family of equivalences} is an ordered family of equivalences
  $\cofe{X}$ such that every Cauchy sequence in $X$ has a limit
  in $X$.
